### 2020-03-04 Common/structure/info.tex
Johan and Julien: Title page updated

\thesistitle{Prostate Cancer Classification:\\A Freeze/Unfreeze Transfer Learning Approach Using Multiple Body Parts} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Prof. Dr. Philippe Cudré-Mauroux} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\cosupervisor{Co-supervisor Name} % If you have a co-supervisor, include it here. This is used in the title page, print it elsewhere with \supname
\degree{Master} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Author Name} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{Bd de Pérolles 90} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

\subject{Computer Science} % Your subject area, this is not currently used anywhere in the template, print it elsewhere with \subjectname
\keywords{keywords, list, here} % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\university{\href{http://www.unifr.ch}{University of Fribourg}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
\department{\href{https://www3.unifr.ch/inf/fr/}{Department of Informatics}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
\group{\href{https://www3.unifr.ch/inf/en/exascale-infolab.html}{eXascale Infolab}} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
\faculty{\href{https://www3.unifr.ch/scimed/fr/}{Faculty of Science and Medicine}} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname

>>>>

\thesistitle{Prostate Cancer Classification:\\A Freeze/Unfreeze Transfer Learning Approach Using Multiple Body Parts} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Prof. Dr. Philippe Cudré-Mauroux} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\cosupervisor{\href{https://exascale.info/members/giuseppe-cuccu/}{Dr. Giuseppe Cuccu},\\ \href{https://exascale.info/members/akansha/}{Akansha Bhardwaj}} % If you have a co-supervisor, include it here. This is used in the title page, print it elsewhere with \supname
\degree{Master} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{\href{mailto:julienclement22@gmail.com}{Julien Clément}, \href{mailto:joh.job13@gmail.com}{Johan Jobin}}% Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{Bd de Pérolles 90} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

\subject{Computer Science} % Your subject area, this is not currently used anywhere in the template, print it elsewhere with \subjectname
\keywords{Prostate cancer classification, Convolutional Neural Networks (CNN), Transfer learning, PROSTATEx, Machine learning, Artificial intelligence} % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\university{\href{http://www.unifr.ch}{University of Fribourg}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
\department{\href{https://www3.unifr.ch/inf/fr/}{Department of Informatics}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
\group{\href{https://www3.unifr.ch/inf/en/exascale-infolab.html}{eXascale Infolab}} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
\faculty{\href{https://www3.unifr.ch/scimed/fr/}{Faculty of Science and Medicine}} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname

### 2020-03-04 Common/structure/title.tex
Johan and Julien: Title page updated

\begin{minipage}[t]{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\
\href{mailto://david.bucher@unifr.ch}{\authorname} % Author name - remove the \href bracket to remove the link
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{flushright} \large
\emph{Supervisor:} \\
\href{https://exascale.info/phil}{\supname} % Supervisor name - remove the \href bracket to remove the link
\\\vspace*{1ex}\emph{Co-Supervisor:} \\ % Remove these two lines if no co-supervisor is involved
\href{https://exascale.info/members/}{\cosupname} % Co-supervisor name - remove the \href bracket to remove the link
\end{flushright}
\end{minipage}\\[1cm]

January 01, 1970 % date of the official defense
\vspace*{.06\textheight}

>>>>

\begin{minipage}[t]{0.4\textwidth}
\begin{flushleft} \large
\emph{Authors:}\\
{\authorname} % Author name - remove the \href bracket to remove the link
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{flushright} \large
\emph{Supervisor:} \\
\href{https://exascale.info/phil}{\supname} % Supervisor name - remove the \href bracket to remove the link
\\\vspace*{1ex}\emph{Co-Supervisors:} \\ % Remove these two lines if no co-supervisor is involved
{\cosupname} % Co-supervisor name - remove the \href bracket to remove the link
\end{flushright}
\end{minipage}\\[1cm]

March XX, 2020 % date of the official defense
\vspace*{.06\textheight}
